Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-06-01 paper_aimsa/introduction.tex
minor ref fix

Various learning algorithms have been tested to be effective for
legged robots. Their studies tested the viability of applying RL
cite{yosinski2011evolvingmethod to legged robot gaits learning. Competitive performance has
been verified on methods such as HyperNEAT \cite{yosinski2011evolving-robot-gaits} and
GA \cite{chernova2004an-evolutionary-approach-to-gait} and other methods \cite{hornby2005autonomous-evolution-of-dynamic} \cite{zykov2004evolving-dynamic-gaits} \cite{tellez2006evolving-the-walking-behaviour} \cite{valsalam2008modular-neuroevolution-for-multilegged}. Despite the excellent performance of these algorithms, a major
part of achieving good performance relies in tuning the parameters for
the evolutionary algorithms \cite{kormushev2011bipedal-walking-energya}. Here we present a
different way for learning gaits using RL (Hill climbing). In our
experiment, it turned out this method achieved competitive performance
with Problem Definition:The gait-learning problem is defined to find a
gait that maximizes some specific metric. Mathematically, we define a
gait as a function that specifies a vector of commanded motor
positions for a robot over time. Gaits without feedback --- also
called open-loop gaits --- can be defined as

>>>>

Various learning algorithms have been tested to be effective for
legged robots. Their studies tested the viability of applying RL
cite{yosinski2011evolvingmethod to legged robot gaits learning. Competitive performance has
been verified on methods such as HyperNEAT \cite{yosinski2011evolving-robot-gaits} and
GA \cite{chernova2004an-evolutionary-approach-to-gait} and other methods \cite{hornby2005autonomous-evolution-of-dynamic} \cite{zykov2004evolving-dynamic-gaits} \cite{tellez2006evolving-the-walking-behaviour} \cite{valsalam2008modular-neuroevolution-for-multilegged}. Despite the excellent performance of these algorithms, a major
part of achieving good performance relies in tuning the parameters for
the evolutionary algorithms \cite{kormushev2011bipedal-walking-energy}. Here we present a
different way for learning gaits using RL (Hill climbing). In our
experiment, it turned out this method achieved competitive performance
with Problem Definition:The gait-learning problem is defined to find a
gait that maximizes some specific metric. Mathematically, we define a
gait as a function that specifies a vector of commanded motor
positions for a robot over time. Gaits without feedback --- also
called open-loop gaits --- can be defined as

### 2012-06-01 paper_aimsa/methods.tex
minor ref fix

Here we used an RL approach to change the complexity of the policy
representation dynamically while the trial is running. In
\cite{kormushev2011bipedal-walking-energya} studies on reducing energy
consumption for bipedal robots, a mechanism that can
evolve the policy parameterization was used. The method starts from a
very simple parameterization and gradually increases its
representational capability. The method tested to be able to generate
an adaptive policy parameterization that can accommodate increasingly
more complex policies. In \cite{kormushev2011bipedal-walking-energya}, the policy
generated by this approach can reach the global optimum at a faster
rate. Also found is that the chance of converging to a suboptimal
solution is reduced, because in the lower-dimensional representation
the effect is less exhibited.

>>>>

Here we used an RL approach to change the complexity of the policy
representation dynamically while the trial is running. In
\cite{kormushev2011bipedal-walking-energy} studies on reducing energy
consumption for bipedal robots, a mechanism that can
evolve the policy parameterization was used. The method starts from a
very simple parameterization and gradually increases its
representational capability. The method tested to be able to generate
an adaptive policy parameterization that can accommodate increasingly
more complex policies. In \cite{kormushev2011bipedal-walking-energy}, the policy
generated by this approach can reach the global optimum at a faster
rate. Also found is that the chance of converging to a suboptimal
solution is reduced, because in the lower-dimensional representation
the effect is less exhibited.
